Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Update on Overleaf.

Fixing the architecture, we performed experiments for the temporal detection task using different values of $k$ and $\gamma$ in the post-processing stage.
Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization performance.
Figures~\ref{fig:example_results_detect} and~\ref{fig:example_results_classification} shows some examples of classification and temporal localization prediction for some instances of the dataset, showing continuous and smooth segments.
% AMAIA: No sé si els exemples de la figura son els millors...no en tens algun on la detecció estigui bé pero la classe no? o al reves? No en vas posar algun a la presentacio de la defensa?
% ALBERTO: Ja he ficat un exemple que passa el que tu dius
% AMAIA: Vist
\begin{figure}[ht]
\centering
\includegraphics[width=1\linewidth]{img/activity_temporal_localization_8.png}
\includegraphics[width=1\linewidth]{img/activity_temporal_localization_55.png}
\includegraphics[width=1\linewidth]{img/activity_temporal_localization_20.png}
%\includegraphics[width=1\linewidth]{img/activity_temporal_localization_35.png}
\caption{Examples of temporal activity localization predictions.}
\label{fig:example_results_detect}
\end{figure}

>>>>

Fixing the architecture, we performed experiments for the temporal detection task using different values of $k$ and $\gamma$ in the post-processing stage.
Table~\ref{table:detection_postprocessing_comparison} shows results for the temporal activity localization task, where the effect of a mean smoothing filter can be seen, improving the localization performance.
Figures~\ref{fig:example_results_detect} and~\ref{fig:example_results_classification} show some examples of classification and temporal localization prediction for some instances of the dataset.
% AMAIA: No sé si els exemples de la figura son els millors...no en tens algun on la detecció estigui bé pero la classe no? o al reves? No en vas posar algun a la presentacio de la defensa?
% ALBERTO: Ja he ficat un exemple que passa el que tu dius
% AMAIA: Vist
\begin{figure}[ht]
\centering
\includegraphics[width=1\linewidth]{img/activity_temporal_localization_8.png}
\includegraphics[width=1\linewidth]{img/activity_temporal_localization_55.png}
\includegraphics[width=1\linewidth]{img/activity_temporal_localization_20.png}
%\includegraphics[width=1\linewidth]{img/activity_temporal_localization_35.png}
\caption{Examples of temporal activity localization predictions.}
\label{fig:example_results_detect}
\end{figure}
